\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-17 public/paper/pyg4ometry.tex
missing word...
we never said what flair is

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\columnwidth]{./model-scene/faradayCup2.pdf}
\caption{Example conversion of a simple FLUKA geometry to GDML. Above:
the original FLUKA geometry displayed in flair. Below: the GDML geometry
viewed using \PYGEOMETRY{}. The example is a Faraday cup used to capture
and measure accelerator beam charge.}
\label{fig:fluka-to-geant4-cup}
\end{center}
\end{figure}

@@

\subsection{Discussion}
Overall the conversion to FLUKA input format from GDML is quite 
advanced and stable. Relatively large experimental simulations 
have been converted from GDML to FLUKA and have been used to produce 
simulation results. The conversion described still requires a user to
understand how geometry is specified in both Geant4 and FLUKA. For 
example the subtraction of many non-primitive body daughter volumes from 
a mother will create a very complex non-DNF region which is inefficient when viewed in 
flair and used for simulation in FLUKA. A geometry designer can avoid this by
restricting daughter volumes solids in Geant4 that can be expressed in DNF simply,
for example a cuboid.  If \PYGEOMETRY{} is used during the creation of
 geometry then multiple codes can be targeted without additional user effort. 
There are still a few outstanding technical issues with the conversion, which are discussed 
in this section.

@@

\PYGEOMETRY{} is principally a toolkit but various visualisation and user interface extensions would 
significantly aid geometry creation workflows. A graphical user interface (GUI) would enable a user without any
 programming experience to create geometry for MCRT simulations and expand the number of potential users.
\PYGEOMETRY{} has been designed to interface with a GUI in a relatively straightforward manner. The VTK visualiser currently 
limits the display of very large models as geometry instances are replicated as opposed to reused in visualisation.  However,
this could be drastically improved in a future release.

@@

\PYGEOMETRY{} is already proving to be a useful tool for geometry conversion, creation and manipulation.
There are numerous international researcher and research groups already using the code for their particular applications.
The users are focused in accelerator physics, but \PYGEOMETRY{} could find application in any scientific
area where MCRT simulations are needed, for example particle physics, space environment and medical physics.
The authors welcome contributions, extensions and bug fixes as well suggestions for larger collaborations.

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\columnwidth]{./model-scene/faradayCup2.pdf}
\caption{Example conversion of a simple FLUKA geometry to GDML. Above:
  the original FLUKA geometry displayed in flair, FLUKA's graphical user interface.
  Below: the GDML geometry viewed using \PYGEOMETRY{}. The example is a Faraday cup used to capture
and measure accelerator beam charge.}
\label{fig:fluka-to-geant4-cup}
\end{center}
\end{figure}

@@

\subsection{Discussion}
Overall the conversion to FLUKA input format from GDML is quite 
advanced and stable. Relatively large experimental simulations 
have been converted from GDML to FLUKA and have been used to produce 
simulation results. The conversion described still requires a user to
understand how geometry is specified in both Geant4 and FLUKA. For 
example the subtraction of many non-primitive body daughter volumes from 
a mother will create a very complex non-DNF region which is inefficient when viewed in 
FLUKA's graphical user interface (GUI), flair, and used for simulation in FLUKA.
A geometry designer can avoid this by
restricting daughter volumes solids in Geant4 that can be expressed in DNF simply,
for example a cuboid.  If \PYGEOMETRY{} is used during the creation of
 geometry then multiple codes can be targeted without additional user effort. 
There are still a few outstanding technical issues with the conversion, which are discussed 
in this section.

@@

\PYGEOMETRY{} is principally a toolkit but various visualisation and user interface extensions would 
significantly aid geometry creation workflows. A graphical user interface would enable a user without any
 programming experience to create geometry for MCRT simulations and expand the number of potential users.
\PYGEOMETRY{} has been designed to interface with a GUI in a relatively straightforward manner. The VTK visualiser currently 
limits the display of very large models as geometry instances are replicated as opposed to reused in visualisation.  However,
this could be drastically improved in a future release.

@@

\PYGEOMETRY{} is already proving to be a useful tool for geometry conversion, creation and manipulation.
There are numerous international researcher and research groups already using the code for their particular applications.
The users are focused in accelerator physics, but \PYGEOMETRY{} could find application in any scientific
area where MCRT simulations are needed, for example particle physics, space environment and medical physics.
The authors welcome contributions, extensions and bug fixes as well as suggestions for larger collaborations.
